Supplementary Figure 1a

### 2017-12-05 inst/lnc34a_cage/lnc34a_cage.Rmd
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

RNAprepTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
    select(`rna extract`) %>%
    count(`rna extract`)
}

localizationTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    select(localization) %>%
    count(localization)
}

@@

#try to cut the data so that the CAGE reads are more visable in the figure.
gdata <- filter(gdata, start < 9245000) %>%
  mutate(stop = if_else(feature == "intron" & start != 9242375, 9245000, stop))

@@

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill, group = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene, group = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.5, label = fill),
    size = 3,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241000, 9245000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

#cage
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray",
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9245000) +
  guides(fill = guide_colourbar(
    title = "RPKM", 
    title.position = "top", 
    title.hjust = 0.5)
  )

#density
p3 <- ggplot(data = NULL) + 
  geom_line(data = cage, aes(x = start), stat = "density") +
  ggthemes::theme_few() +
  xlim(9241000, 9245000) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Density")

@@

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray",
    lwd = 0.1
  ) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 0.25
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.55, label = fill),
    size = 1.75,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241000, 9245000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE) +
  theme(
    axis.text = element_text(size = 6),
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 6, margin = margin(r = 8, "cm")),
    axis.ticks.length = unit(0.5, "mm"),
    axis.ticks = element_line(size = 0.15),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
  )

#cage
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = NA,
    lwd = 0.1,
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 6),
    legend.position = "top",
    legend.title = element_text(size = 5),
    legend.text = element_text(size = 4),
    legend.box.spacing = unit(3, "pt"),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
    strip.text.y = element_text(angle = 0)
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9245000) +
  guides(fill = guide_colourbar(
    title = "RPKM", 
    title.position = "top", 
    title.hjust = 0.5,
    barheight = unit(2, "mm")
  ))

#density
p3 <- ggplot(data = NULL) + 
  geom_line(
    data = cage, 
    aes(x = start), 
    stat = "density", 
    lwd = 0.1
  ) +
  ggthemes::theme_few() +
  xlim(9241000, 9245000) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 6),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1)
    #plot.margin = unit(c(0, 1, 2, 1), "mm")
  ) +
  labs(y = "Density")

>>>>

RNAprepTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
    select(`rna extract`) %>%
    dplyr::count(`rna extract`)
}

localizationTable <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    select(localization) %>%
    dplyr::count(localization)
}

@@

#try to cut the data so that the CAGE reads are more visable in the figure.
gdata <- filter(gdata, start < 9243000) %>%
  mutate(stop = if_else(feature == "intron", 9243000, stop))

@@

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill, group = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene, group = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.5, label = fill),
    size = 3,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241596, 9243000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

#cage
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray",
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Cage reads") +
  xlim(9241596, 9243000) +
  guides(fill = guide_colourbar(
    title = "RPKM", 
    title.position = "top", 
    title.hjust = 0.5)
  )

#density
p3 <- ggplot(data = NULL) + 
  geom_line(data = cage, aes(x = start), stat = "density") +
  ggthemes::theme_few() +
  xlim(9241596, 9243000) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Density")

@@

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(gdata, feature %in% c("exon", "primer")),
    aes(xmin = start, xmax = stop, y = gene, fill = fill),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray",
    lwd = 0.1
  ) +
  geom_segment(
    data = filter(gdata, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 0.55
  ) +
  geom_text(
    data = filter(gdata, feature == "primer"),
    aes(x = start + 10, y = 2.55, label = fill),
    size = 1.75,
    angle = 90,
    colour = "grey20"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  xlim(9241596, 9243000) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE) +
  theme(
    axis.text = element_text(size = 6),
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 6, margin = margin(r = 8, "cm")),
    axis.ticks.length = unit(0.5, "mm"),
    axis.ticks = element_line(size = 0.15),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
  )

#cage
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = NA,
    lwd = 0.1,
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 6),
    legend.position = "top",
    legend.title = element_text(size = 5),
    legend.text = element_text(size = 4),
    legend.box.spacing = unit(3, "pt"),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
    strip.text.y = element_text(angle = 0)
  ) +
  labs(y = "Cage reads") +
  xlim(9241596, 9243000) +
  guides(fill = guide_colourbar(
    title = "RPKM", 
    title.position = "top", 
    title.hjust = 0.5,
    barheight = unit(2, "mm")
  ))

#density
p3 <- ggplot(data = NULL) + 
  geom_line(
    data = cage, 
    aes(x = start), 
    stat = "density", 
    lwd = 0.1
  ) +
  ggthemes::theme_few() +
  xlim(9241596, 9243000) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 6),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1)
    #plot.margin = unit(c(0, 1, 2, 1), "mm")
  ) +
  labs(y = "Density")

### 2017-12-05 inst/p1_hek293t/p1_hek293t.Rmd
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = shRNA,
      y = log2fold,
      group = interaction(shRNA, GOI)
    ),
    trim = TRUE,
    alpha = 0.5,
    fill = "grey",
    colour = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = shRNA,
      y = log2fold,
      fill = GOI,
      group = interaction(shRNA, GOI)
    ),
    binwidth = 1/10,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  facet_grid(. ~ belongsTo) +
  scale_y_continuous("\u0394\u0394Ct")+
  labs(x = "shRNA")

>>>>

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = shRNA,
      y = log2fold,
      group = interaction(shRNA, GOI)
    ),
    trim = TRUE,
    alpha = 0.5,
    fill = "grey",
    colour = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = shRNA,
      y = log2fold,
      fill = GOI,
      group = interaction(shRNA, GOI)
    ),
    binwidth = 1/10,
    colour = NA,
    alpha = 0.75,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 3,
    show.legend = TRUE
  ) +
  facet_grid(. ~ belongsTo, scales = "free") +
  scale_y_continuous("\u0394\u0394Ct")+
  labs(x = "shRNA")

### 2017-12-05 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.1
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.2,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  )

@@

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.3
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    shape = 95,
    size = 4
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43",
    size = 0.3
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.2,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  )

@@

<br></br><br></br>

```{r}
sessionInfo()
```

### 2017-12-05 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

pdf <- p + 
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.4,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  ) +
   geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20",
    size = 0.1
  )

>>>>

pdf <- p + 
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    shape = 95,
    size = 4
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43",
    size = 0.3
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.4,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  ) +
   geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20",
    size = 0.3
  )

### 2017-12-05 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

p <- ggplot(data = NULL)+
  geom_violin(
    data = data,
    aes(
      x = Condition,
      y = log2fold
    ),
    scale = "width",
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = Condition, 
      y = log2fold, 
      fill = Condition
    ),
    colour = NA,
    binwidth = 1/10,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis='y', 
    stackdir='center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  facet_grid(. ~ `Cell line`, scales = "free") +
  labs(
    x = "Cell line",
    y = "log2(Fold)",
    title = "miR34a asRNA"
  ) +
  guides(fill = FALSE)

@@

pdf <- p +
  geom_point(
    data = stats,
    aes(
      x = Condition, 
      y = mean
    ),
    colour = "grey20",
    show.legend = FALSE,
    shape = 95
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Condition, 
      ymin = CI95l, 
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  )

>>>>

p <- ggplot(data = NULL)+
  geom_violin(
    data = data,
    aes(
      x = Condition,
      y = log2fold
    ),
    scale = "width",
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = Condition, 
      y = log2fold, 
      fill = Condition
    ),
    colour = NA,
    binwidth = 1/10,
    alpha = 0.75,
    position = position_dodge(width = 0.9), 
    binaxis='y', 
    stackdir='center',
    dotsize = 6,
    show.legend = TRUE
  ) +
  facet_grid(. ~ `Cell line`, scales = "free") +
  labs(
    x = "Cell line",
    y = "log2(Fold)",
    title = "miR34a asRNA"
  ) +
  guides(fill = FALSE)

@@

pdf <- p +
  geom_point(
    data = stats,
    aes(
      x = Condition, 
      y = mean
    ),
    colour = "grey20",
    show.legend = FALSE,
    size = 4,
    shape = 95
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Condition, 
      ymin = CI95l, 
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.3,
    show.legend = FALSE
  )

### 2017-12-05 inst/tcga_correlation_table/tcga_correlation_table.Rmd
more work on figure readability, done?

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer_PAM50) %>%
  summarize(
    n = n(),
    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer_PAM50, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer_PAM50:TP53)) %>%
  unite(temp, TP53, metric) %>%
  spread(temp, value)

full_join(all, p53, by = "cancer_PAM50")
```

>>>>

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer_PAM50) %>%
  summarize(
    n = n(),
    `all p` = cor.test(RP3, miR34a, method = "spearman")$p.value,
    `all rho` = cor.test(RP3, miR34a, method = "spearman")$estimate
  ) %>%
  mutate(
    `all p` = format(`all p`, scientific = TRUE, digits = 3),
    `all rho` = format(`all rho`, scientific = TRUE, digits = 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer_PAM50, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    p = cor.test(RP3, miR34a, method = "spearman")$p.value,
    rho = cor.test(RP3, miR34a, method = "spearman")$estimate
  ) %>%
  ungroup() %>%
  mutate(
    p = format(p, scientific = TRUE, digits = 3),
    rho = format(rho, scientific = TRUE, digits = 3)
  ) %>%
  gather(metric, value, -(cancer_PAM50:TP53)) %>%
  unite(temp, TP53, metric, sep = " ") %>%
  spread(temp, value)

table <- full_join(all, p53, by = "cancer_PAM50") %>%
  rename(cancer = cancer_PAM50, `all n` = n) %>%
  select(
    cancer, `all n`, `all rho`, `all p`, `TP53wt n`, 
    `TP53wt rho`, `TP53wt p`, `TP53mut n`, `TP53mut rho`, `TP53mut p`
  )

table

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1a"][[1]])
# pdf(file = path, width = 14)
# gridExtra::grid.table(table, rows = NULL)
# invisible(dev.off())
```
